---
title: "Analyses for COVID-19 impact on Routine Immunisation in 2020"
author: "Beth Evans and Thibaut Jombart"
date: "1 Dec 2021"
output: 
  html_document:
    code_folding: "show"
    toc: TRUE
    toc_depth: 4
    toc_float: TRUE
    toc_collapse: FALSE
    number_sections: TRUE
    highlight: pygments
    theme: spacelab
params:
  data: "dtp1"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      dev = c("png", "pdf"),
                      fig.path = "figs/",
                      dpi = 100)
```

# Set-up

## Load packages

```{r, message = FALSE}
library(tidyverse)
library(rio)
library(magrittr)
library(timetk)
library(broom)
library(scales)
library(ggforce)
library(urca)
library(tseries)
library(forecast)
library(data.table)
library(countrycode)
library(here)
library(flextable)
library(webshot)
library(wesanderson)
library(cowplot)

```

## Load raw data

Import data:

- Coverage data from WUENIC for 2000-2020
- Income group classification from World Bank
- Birth and infant mortality data from United Nations World Population Prospects
  (UN WPP)

```{r}
# Set-up toggle to pull DTP1 and DTP3 data respectively when compiling for the
# appropriate antigen
if (params$data == "dtp1") {
  file_path <- here::here("data", "dtp1_oct.csv")
} else if (params$data == "dtp3") {
  file_path <- here::here("data", "dtp3_oct.csv")
} else {
  msg <- sprintf("Unknown dataset requested: %s", params$data)
  stop(msg)
}

# Impact WUENIC data
data_raw <- file_path %>%
  rio::import(header = TRUE) %>%
  tibble()
data_raw

# Import World Bank classification data
file_path_wb <- here::here("data", "wb_ig.csv")
income <- file_path_wb %>%
  rio::import(header = TRUE) %>%
  tibble()
income

# Import UN WPP data
file_path_unwpp_raw <- here::here("data", "WPP2019_INT_F01_ANNUAL_DEMOGRAPHIC_INDICATORS.csv")

unwpp_raw <- file_path_unwpp_raw %>%
  rio::import(header = TRUE, skip = 16) %>%
  tibble()

unwpp_raw

```

## Set-up output folders

Outputs are stored in two separate folders (in addition to the compiled report,
handled by the *reportfactory*), *outputs/figures/* and *outputs/csv/*. We make
sure these exist.

```{r}
# Make sure output folder exists
fig_folder <- here::here("figures", params$data)
if (!dir.exists(fig_folder)) {
  dir.create(fig_folder, recursive = TRUE)
}

# Make sure output folder exists
csv_folder <- here::here("outputs", "csv", params$data)
if (!dir.exists(csv_folder)) {
  dir.create(csv_folder, recursive = TRUE)
}

```



# Data preparation

Here we prepare the dataset analysed called `x`.

## Data cleaning

Steps taken:

- rename variables 
- reshape data to long vs. wide format
- add categorisation columns (income group, region)
- select relevant columns only 

```{r}

# Clean and reshape 2000-2020 coverage data
data_clean <- data_raw %>% 
  rename(iso_code = iso3) %>%
  mutate(region = countrycode(iso_code,
                              origin = "iso3c",
                              destination = "un.region.name")) %>%
  select(region, unicef_region, everything())

data_long <- data_clean %>%
  pivot_longer(-(region:vaccine), names_to = "year", values_to = "coverage")
names(data_long) <- tolower(names(data_long))
data_long

# Join 'income' classification to main dataset
income %<>% 
  filter(datayear == "2020") %>%
  dplyr::rename(iso_code = wb_code) %>%
  dplyr::select(-c(datayear, country, fiscalyear, publicationyear))
income

data_long %<>%
  inner_join(income, by = "iso_code")
data_long

# Clean consolidated projection dataset
x <- data_long %>%
  mutate(coverage = coverage / 100,
         year = as.integer(year),
         income_group = recode_factor(income_group,
                                      "Low income" = "LIC",
                                      "Lower middle income" = "LMIC",
                                      "Upper middle income" = "UMIC",
                                      "High income" = "HIC")        
         ) %>%
  select(region, country, iso_code, income_group, year, coverage) %>%
  arrange(country, year)
x

```


## Data filtering

We remove:

- years prior to 2000
- entries where coverage is NA
- countries without data for the last 21 consecutive years (from 2000 to 2020,
  inclusive)

```{r}

# Filter for data from 2000 onwards (inclusive), remove NAs
x <- x %>%
  filter(year >= 2000, !is.na(coverage))

# Filter for countries with complete data from 2000 to 2020, i.e. 21 data points
complete_countries <- x %>%
  count(iso_code) %>%
  filter(n == 21) %>%
  pull(iso_code)

x %<>%
  filter(iso_code %in% complete_countries)

```


# ARIMA modelling

Here we apply ARIMA to each country using the years 2000-2019 as training set,
and derive a forecast for 2020 with associated confidence intervals. The final
object will be called `res`, and will include these forecasts, the actual values
reported, and the corresponding coverage *deltas*, defined as (% reported - %
expected).

## Model parameters

Model "expected' 2020 coverage based, in the absence of COVID, based on
2000-2019 trends.  ARIMA model uses timeseries data by country to (a) select the
most appropriate model, defined by three parameters (p, d, q) selected as
follows:

- p = number of autoregressive terms - based on minimisation of the AIC
- d = number of non-seasonal differences needed for stationarity - based on conducting KPSS tests
- q = number of lagged forecast errors in the prediction equation - based on minimisation of the AIC

and (b) predict 2020 coverage based on this selected model.


## Fitting models

`auto.arima` requires time series (`ts`) objects, which is essentially a wide
format for coverage data (rows = years, columns = countries)..

```{r}

# Reshape data to timeseries format
ts_df <- x %>%
  filter(year < 2020) %>% 
  select(year, iso_code, coverage) %>%
  pivot_wider(values_from = coverage, names_from = iso_code) %>%
  arrange(year) %>%
  select(-year) %>% 
  ts(start = 2000, freq = 1)

# ARIMA forecast 2020 coverage from 2000-2019 data for all countries
ts_forecasts <- lapply(ts_df, # iterate over all countries
                      function(y)
                        forecast(auto.arima(y, seasonal = FALSE),
                                 h = 1, # forecast 1 year ahead
                                 level = 95 # 95% CIs
                                 ))

# extract forecasts and format output
temp <- lapply(ts_forecasts,
               function(e) c(method = e$method, as.data.frame(e)))

forecasts <- bind_rows(temp) %>%
  mutate(iso_code = names(temp),
         mean = `Point Forecast`,
         lower_ci = `Lo 95`,
         upper_ci = `Hi 95`) %>%
  tibble() %>%
  select(iso_code, method, mean, lower_ci, upper_ci)
forecasts

```

Since WUENIC coverage is capped at 99% (i.e., no country can ever report 100%)
we replace any 2020 estimates >99% to 99% coverage; also make sure CI don't go
below 0.

```{r}

forecasts <- forecasts %>%
  mutate(mean = if_else(mean > 0.99, 0.99, mean),
         lower_ci = if_else(lower_ci < 0, 0, lower_ci),
         upper_ci = if_else(upper_ci > 0.99, 0.99, upper_ci),)

```


## Combine ARIMA predictions and 2020 data

Here we add the model prediction to the data, keeping only 2020, and calculate
deltas (coverage values in 2020: % reported - % expected) and associated
confidence intervals.

```{r}

res_all <- forecasts %>%
  left_join(x) %>%
  filter(year == 2020) %>% 
  mutate(delta = coverage - mean,
         lower_delta = coverage - lower_ci,
         upper_delta = coverage - upper_ci,
         within_ci = (coverage >= lower_ci) & (coverage <= upper_ci),
         ci_width = upper_ci - lower_ci
         )

```


## Remove unreliable expected coverage estimates

Countries were considered as potential unreliable datapoints based on:

1. Visual inspection of 2000-2019 WUENIC reported coverage showed high
volatility, i.e., fluctuations over a 10-percentage point range in the last
five to 10 years – since this indicates coverage estimates may be unreliable
and uncertain

2. Visual inspection of forecast model fit showed fit dependent on major
increases/ decreases in 2018-2019 coverage – since this indicates exceptional
circumstances (e.g., stockouts, civil war) may have overly weighted forecast
coverage

3. Calculating forecast percentage point improvement in coverage from reported
2019 to forecast 2020 coverage and reviewing countries with forecast +5
percentage point improvements – since such may not be programmatically realistic
(despite model fitting)

Then, WUENIC country-specific documentation was reviewed to confirm whether to
remove countries.

For option (3):

```{r}

# Filter out countries with >5p.p. improvement
res <- res_all %>%
  filter(delta <= 0.05)
res

```

Countries considered as potential unreliable estimated coverage estimates are
detailed with explanations in the Supplementary Materials.


## Remove countries identified as unreliable datapoints

```{r}

# Default is to remove no countries
removed_countries <- NULL

# Removed countries for DTP1
if (params$data == "dtp1") {
  removed_countries <- c("Haiti", "Libya", "Samoa", "Solomon Islands", "Brazil",
                         "Jordan", "Bolivia (Plurinational State of)",
                         "Suriname", "Austria")
}

# Removed countries for DTP3
if (params$data == "dtp3") {
  removed_countries <- c("Haiti", "Libya", "Samoa", "Solomon Islands", "Brazil",
                         "El Salvador", "Jordan", "Malawi",
                         "Venezuela (Bolivarian Republic of)", "Suriname")
}

# Keep track of removed countries
res_removed_countries <- res_all %>%
  dplyr::filter(country %in% removed_countries)
x_removed_countries <- x %>%
  dplyr::filter(country %in% removed_countries)

# Remove countries from dataset for further analysis
res <- res %>%
  dplyr::filter(!country %in% removed_countries)

```


#### Plot of removed datapoints

```{r fig_removed_countries, results = "hide", fig.keep = 1, fig.width = 10, fig.height = 10, out.width = "100%"}

# Define color for model
arima_color <- "#ac3973"

# Generate plot
fig_removed_countries <- x_removed_countries %>%
  ggplot(aes(x = year, y = coverage)) +
  theme_bw() +
  geom_point(alpha = 0.8) +
  geom_line(alpha = 0.3) +
  geom_errorbar(data = res_removed_countries,
                aes(ymin = lower_ci, ymax = upper_ci),
                color = arima_color) +
  geom_point(data = res_removed_countries,
             aes(y = mean), shape = 3, color = arima_color) +
  facet_wrap(~ country, scales = "free_y",
             labeller = label_wrap_gen(25)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L), 
                     limits = c(NA,1),
                     n.breaks = 5) +
  labs(title = "Countries removed from further analysis - unreliable ARIMA",
       y = "Coverage (%)",
       x = "Year") +
  theme(axis.text.x = element_text(angle=45,hjust = 1, size = 14),
        axis.text.y = element_text(size = 14), 
        strip.text.x = element_text(size = 14), 
        axis.title = element_text(size = 18))

fig_removed_countries

# Save file
ggsave(filename = here::here(fig_folder, "forecast_removed_countries.png"),
       plot = fig_removed_countries, 
       width = 30, height = 30, units = "cm")

```



## Plot and visualise coverage timeseries

This reproduces the figure from the paper using the 4 largest countries as an
example of reported coverage values vs ARIMA model prediction.

```{r fig_large_pops, out.width = "100%", fig.width = 10, fig.height = 3}

# Select countries for inclusion in plot
large_pops <- c("India", "Pakistan", "Indonesia", "Philippines", "Mexico")

x_large <- x %>%
  filter(country %in% large_pops)

res_large <- res %>%
  filter(country %in% large_pops)

# Generate plot
arima_color <- "#ac3973"

fig_large_pops <- ggplot(data = x_large, aes(x = year, y = coverage)) +
  theme_bw() +
  geom_point(alpha = 0.8) +
  geom_line(alpha = 0.3) +
  geom_errorbar(data = res_large, aes(ymin = lower_ci, ymax = upper_ci),
                color = arima_color) +
  geom_point(data = res_large, aes(y = mean), shape = 3, color = arima_color) +
  facet_wrap(~ country, nrow = 1, scales = "free_y",
             labeller = label_wrap_gen(25)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L), 
                     limits = c(NA,1),
                     n.breaks = 5) +
  labs(y = "Coverage (%)",
       x = "Year") +
  theme(axis.text.x = element_text(angle=45,hjust = 1, size = 14),
        axis.text.y = element_text(size = 14), 
        strip.text.x = element_text(size = 14), 
        axis.title = element_text(size = 18))
 
fig_large_pops

# Save file 
ggsave(filename = here::here(fig_folder, "forecast_large_pops.png"),
       plot = fig_large_pops, 
       width = 30, height = 10, units = "cm")

```





<br>

# Investigating differences in coverage

In this section we analyse the differences between reported and expected
coverage, in general and across different strata. Note that making a pairwise
t-test between the reported and expected coverage is identical to testing deltas
against the null hypothesis that delta = 0. For simplicity, we do the
latter. Simple ANOVAs will be used when comparing deltas across strata.

## t-test for all countries combined

```{r}

# Conduct t-test
ttest_total <- t.test(res$delta,
                      alternative = "two.sided")
ttest_total

# Create readable output of t-test results
stats_total <- res %>%
  summarise(reported = mean(coverage),
            expected = mean(mean))

tt_total <- tibble(stats_total, broom::tidy(ttest_total))
tt_total

# Save output
write.csv(
  tt_total,
  here::here(csv_folder, "ttest_total.csv"),
  row.names = FALSE)

```

We represent a corresponding scatterplot. Red dots indicate countries for which
the 95% CI of delta excludes zero.

```{r fig_overall_results, fig.width = 8, fig.height = 8}

fig_overall_results <- res %>% 
  ggplot(aes(x = mean, y = coverage)) +
  geom_pointrange(alpha = .4, aes(xmin = lower_ci, xmax = upper_ci, color = within_ci)) +
  #geom_point(alpha = .4, size = 3, aes(color = within_ci)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) + 
  scale_x_continuous(labels = unit_format(unit = "%", scale = 1e+2)) +
  scale_y_continuous(labels = unit_format(unit = "%", scale = 1e+2)) +
  scale_color_manual(guide = FALSE,
                     values = c(`TRUE` = "black",
                                `FALSE` = "#e63553")) +
  labs(x = "Expected coverage in 2020",
       y = "Actual coverage in 2020") +
  theme_light() +
  theme(plot.title = element_text(face = "bold", size = 20),
        legend.position = "none",
        axis.text = element_text(size = 12),
        axis.title.y = element_text(angle = 90),
        axis.title = element_text(size = 17)
  )

fig_overall_results

# Save file
ggsave(filename = here::here(fig_folder, "overall_results.png"),
       plot = fig_overall_results, 
       width = 15, height = 15, units = "cm")

```


## Analyses by region

Here we perform an ANOVA and associated boxplot by region.

```{r}

# linear model
lm_region <- lm(delta ~ -1 + region, data = res)

# ANOVA
anova(lm_region)

# Tests on individual coefficients
ttest_regions <- lm_region %>%
  summary() %>%
  tidy()

# Create readable output
stats_regions <- res %>%
  group_by(region) %>%
  summarise(reported = mean(coverage),
            expected = mean(mean),
            delta = mean(delta))

# Confidence intervals (95%)
ci_regions <- lm_region %>%
  confint() %>%
  as.data.frame() %>%
  setNames(c("lower_ci", "upper_ci")) %>%
  tibble()

tt_regions <- tibble(stats_regions, ci_regions, ttest_regions)
tt_regions

# Save output
write.csv(
  tt_regions,
  here::here(csv_folder, "ttest_region.csv"),
  row.names = FALSE)

```

We generate a boxplot by region:

```{r boxplot_region}

# Generate region box plot
n_regions <- res %>%
  pull(region) %>%
  unique() %>%
  length()
region_pal <- wes_palette("Darjeeling1", n_regions, type = "discrete")

fig_region <- ggplot(res,
                 aes(x = region, y = delta, color = region)) +
  geom_boxplot(aes(color = region)) +
  geom_point(size = 2, position = position_jitter(width = 0.2), alpha = .5) +
  scale_colour_manual(values = region_pal) +
  stat_summary(fun = mean, geom = "point", shape = 4, size = 4, color = region_pal) +
  scale_y_continuous(labels = unit_format(unit = "%", scale = 1e+2)) +
  labs(x = "",
       y = "Change in coverage (reported - expected)") +
  theme_light() +
  theme(legend.position = "none",
        axis.text = element_text(size = 14),
        axis.title.y = element_text(angle = 90),
        axis.title = element_text(size = 17)) +
  scale_x_discrete(labels = wrap_format(12)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", colour = "black", size = 1)

fig_region

# Save file
ggsave(filename = here::here(fig_folder, "region_box_plot.png"),
       plot = fig_region, 
       width = 30, height = 15, units = "cm")

```



## ANOVA by income

Here we perform an ANOVA and associated boxplot by income group.

```{r}

# remove countries with no income group
res_no_missing_income <- res %>%
  filter(income_group != "") %>%
  droplevels()

# linear model
lm_income <- lm(delta ~ -1 + income_group,
                 data = res_no_missing_income)

# ANOVA
anova(lm_income)

# Tests on individual coefficients
ttest_incomes <- lm_income %>%
  summary() %>%
  tidy()

# Create readable output
stats_incomes <- res_no_missing_income %>%
  group_by(income_group) %>%
  summarise(reported = mean(coverage),
            expected = mean(mean),
            delta = mean(delta))

# Confidence intervals (95%)
ci_incomes <- lm_income %>%
  confint() %>%
  as.data.frame() %>%
  setNames(c("lower_ci", "upper_ci")) %>%
  tibble()

tt_incomes <- tibble(stats_incomes, ci_incomes, ttest_incomes)
tt_incomes

# Save output
write.csv(
  tt_incomes,
  here::here(csv_folder, "ttest_incomes.csv"),
  row.names = FALSE)

```

We generate a boxplot by income group:

```{r boxplot_income}

# Generate income group box plot
n_income <- res_no_missing_income %>%
  pull(income_group) %>%
  unique() %>%
  length()
income_pal <- wes_palette("BottleRocket2", n_income, type = "discrete")

# Generate income group box plot
fig_income <- ggplot(res_no_missing_income,
                     aes(x = income_group, y = delta, color = income_group)) +
  labs(x = "",
       y = "Change in coverage (reported - expected)") +
  scale_y_continuous(labels = unit_format(unit = "%", scale = 1e+2)) +
  geom_boxplot() +
  geom_point(size = 2, position = position_jitter(width = 0.2), alpha = .5) +
  scale_colour_manual(guide = FALSE, values = income_pal) +
  stat_summary(fun = mean, geom = "point", shape = 4, size = 4, color = income_pal) +
  theme_light() +
    theme(legend.position = "none",
        axis.text = element_text(size = 14),
        axis.title.y = element_text(angle = 90),
        axis.title = element_text(size = 17)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", colour = "black", size = 1)

fig_income

# Save file
ggsave(filename = here::here(fig_folder, "income_box_plot.png"),
       plot = fig_income, 
       width = 30, height = 15, units = "cm")

```

## ANOVA by region and income

We check if deltas still differ by region after accounting for the effect of
income.

```{r}

# check link between income group and region using simulated Chi-square
table(
  res_no_missing_income$income_group,
  res_no_missing_income$region) %>%
  chisq.test(simulate.p.value = TRUE, B = 1e5)

# effect of region after accounting for income
lm_income_region <- lm(delta ~ income_group + region,
                       data = res_no_missing_income)

# ANOVA
lm_income_comparable <- lm(delta ~ income_group,
                           data = res_no_missing_income)

anova(lm_income_region, lm_income_comparable)

# effect of income after accounting for region
lm_region_income <- lm(delta ~ region + income_group,
                       data = res_no_missing_income)

# ANOVA
# note: we need to re-fit a model with region effect with the same dataset used
# for income to ensure models are comparable
lm_region_comparable <- lm(delta ~ region,
                           data = res_no_missing_income)
anova(lm_region_income, lm_region_comparable)


```
We generate manuscript figure illustrating income and region trends adjacent:

```{r}
heterogeneity_fig <- plot_grid(fig_region, fig_income,
                    labels = c("A", "B"))
heterogeneity_fig

ggsave(filename = here::here(fig_folder, "heterogeneity_fig.png"),
       plot = heterogeneity_fig, 
       width = 30, height = 15, units = "cm")
```



<br>

# Estimating missed immunisation

In this section we estimate missed immunisation using UNWPP data, by applying
the changes in coverage estimated to the current estimates of infant
populations.

We will:

- clean UNWPP data
- clean UNWPP data to calculate surviving infants in 2020 (target populations
  for DTP1 and DTP3 vaccination)
- estimate infant populations as: number of births - number of infants that die
  < age 1


## Clean UNWPP data

```{r}

unwpp <- unwpp_raw %>% 
  rename(country = "Region, subregion, country or area *",
         country_code = "Country code",
         infant_deaths = "Infant deaths, both sexes combined (under age 1, thousands)",
         births = "Births (thousands)",
         year = "Reference date (1 January - 31 December)") %>%
  filter(Type == "Country/Area",
         year == 2020) %>%
  select(country, country_code, infant_deaths, births) %>%
  mutate(births = as.numeric(str_replace_all(births," ", "")),
         infant_deaths = as.numeric(infant_deaths),
         iso_code = countrycode(sourcevar = country_code,
                                origin = "iso3n",
                                destination = "iso3c"),
         surviving_infants = (births-infant_deaths) * 1000) %>%
  dplyr::select(iso_code, surviving_infants)

unwpp

```


## Calculate missed immunisations

- We multiply coverage delta estimates by surviving infant populations to
calculate additional missed immunisations

```{r}

# Calculate missed immunisations
res_missed <- res %>% 
  left_join(unwpp, by = "iso_code") %>%
  mutate(additional_missed = as.integer(surviving_infants * -delta),
         additional_missed_low = as.integer(surviving_infants * -lower_delta),
         additional_missed_high = as.integer(surviving_infants * -upper_delta ),
         expected_missed = round((1 - mean) * surviving_infants),
         total_missed = round((1 - coverage) * surviving_infants))
res_missed

```

## Format output table

We rename and reformat `res_missed` for an output to Excel:

```{r}

# Create summary output in cleaned format
summary_output <- res_missed %>%
  mutate(coverage = percent(coverage, accuracy = 0.1),
         mean = percent(mean, accuracy = 0.1),
         delta = percent(delta, accuracy = 0.1)) %>%
  dplyr::select(country, iso_code, region, region, income_group,
                mean,
                lower_ci, upper_ci, ci_width,
                coverage, delta, lower_delta, upper_delta,
                within_ci, surviving_infants,
                total_missed, expected_missed, 
                additional_missed,
                additional_missed_low,
                additional_missed_high) %>%
  rename(Country = country,
         "ISO code" = iso_code,
         "UN region" = region,
         "Income group" = income_group,
         "ARIMA modelled expected 2020 coverage (mean)" = mean,
         "ARIMA modelled expected coverage (min 95% CI)" = lower_ci,
         "ARIMA modelled expected coverage (max 95% CI)" = upper_ci,
         "ARIMA coverage 95% CI" = ci_width,
         "WUENIC reported 2020 coverage" = coverage,
         "Delta (expected - reported, mean)" = delta,
         "Delta (expected - reported, min 95% CI)" = lower_delta,
         "Delta (expected - reported, max 95% CI)" = upper_delta,
         "WUENIC-reported coverage within ARIMA-predicted 95% CI" = within_ci,
         "Surviving infants" = surviving_infants,
         "Additional missed immunisations (mean)" = additional_missed,
         "Additional missed immunisations (max 95% CI)" = additional_missed_high,
         "Additional missed immunisations (min 95% CI)" = additional_missed_low,
         "Expected missed children" = expected_missed,
         "Total missed immunisations" = total_missed)

# Save file
write.csv(
  summary_output,
  here::here(csv_folder, "summary_output.csv"),
  row.names = FALSE)

```



<br>

# Tables for manuscript

In this section we generate various tables for the manuscript and supplementary
material.

## Table 1

This table is included in the main text.

```{r}

border_style <- officer::fp_border(color="black", width=1)

table_output <- summary_output %>%
  arrange(desc(`Additional missed immunisations (mean)`)) %>%
  head(10) %>%
    mutate(`ARIMA modelled expected 2020 coverage [95% CI]` = 
           paste(`ARIMA modelled expected 2020 coverage (mean)`,
                 " [",percent(as.numeric(`ARIMA modelled expected coverage (max 95% CI)`), 
                              accuracy = 0.1)
                 ,"; ",percent(as.numeric(`ARIMA modelled expected coverage (min 95% CI)`), 
                               accuracy = 0.1),"]",
                 sep = "")) %>%
    rename(`Change in coverage (mean)` = `Delta (expected - reported, mean)`) %>%
  select(Country, `ISO code`, `UN region`, `Income group`,
         `ARIMA modelled expected 2020 coverage [95% CI]`, `WUENIC reported 2020 coverage`,
         `Change in coverage (mean)`, `Total missed immunisations`,
         `Additional missed immunisations (mean)`) %>%
  flextable() %>% 
  width(j=c(3, 4, 6, 7), width = 1) %>%
  width(j=1, width = 1.1) %>%
  width(j=2, width = 0.5) %>%
  width(j=5, width = 2) %>%
  width(j=c(8, 9), width = 1.25) %>%
  theme_booktabs() %>%
  bold(bold = TRUE, part = "header") %>%
  vline(part = "all", j = 4, border = border_style) %>%
  vline(part = "all", j = 7, border = border_style)

table_output

save_as_docx("Modelled coverage declines and missed immunisations for 10 countries with greatest absolute increases in missed immunisations" = table_output, path = "../figures/top10_table.docx")
save_as_image(table_output, path = "../figures/top10_table.png", webshot = "webshot")

```


## ARIMA summary table

Produce table showing order and fit of all ARIMA models per country

```{r}
# Generate summary table showing ARIMA model fit
arima_table <- res %>%
  mutate(mean = percent(as.numeric(mean), accuracy = 0.1),
         lower_ci = percent(as.numeric(lower_ci), accuracy = 0.1),
         upper_ci = percent(as.numeric(upper_ci),accuracy = 0.1)) %>%
  rename(Country = country,
         "ISO code" = iso_code,
         "ARIMA model fit" = method,
         "Expected 2020 coverage" = mean,
         "Expected: 95% Confidence interval - lower bound" = lower_ci,
         "Expected: 95% Confidence interval - upper bound" = upper_ci)

# Save file
write.csv(
  arima_table,
  here::here(csv_folder, "ARIMA_models.csv"),
  row.names = FALSE)

```
